Changelog

### 2021-05-25 changelog.tex
Updates from Overleaf

I have a few choices to address the limitation. First, I can use static analysis (model checking or static program analysis). Although I am interested in static analysis, I am not a big fan of current static analysis tools, especially for side-channel research. There are many papers on static side-channel analysis. Nearly all of these tools are used to prove the absence of side-channel leakages. However, most of them have high false-positive rates.

On the other hand, there are many success stories with dynamic tools (e.g., SAGE, AFL, Valgrind) in recent years. In particular, fuzzing is becoming a hot trend these years, especially after DARPA CGC in 2016. The fuzzing method is suitable for a task such as side-channel detection. If a program executes two different code paths or accesses two different addresses with two different input values, the program is vulnerable to side-channel attacks. When we report the leakages sites to developers, we can tell them the two inputs. Developers can quickly reproduce the leakage sites with the inputs.  Interestingly, there are a few (not many) related papers. That's why I used fuzzing at the beginning of the project.

@@

It is possible to extend the quantification part to include other side-channel signals (e.g., Sound, CPU usages, EM signals). The key is to model the noises properly. In my dissertation, we assume that an attacker can have a noise-free observation. While a noise-free observation is possible for some address-based side-channel attacks, the assumption is too ideal for many other side-channel attacks. The good news is that there are some mature methods in information theory to model the noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a computable method to estimate the information that can be reliably transferred over a channel between secret data and attackers' observations. From a research project aspect, I hope to have a stronger motivation before starting the project. 
\item \textbf{A bits vs. Q bits. Lower bounds?
       Improve the presentation
       Make the comparison more meaningful
       Etc.}

@@

c. I agree with Dr. Liu's comments that the quantification metrics in Chapter 4 and Chapter 5 are different. The reason that I compare them together in Table 5.3 is that they have the same dimensional unit (bit) under the dimensional analysis. I have removed the comparison in the current version.

@@

a. I revised the description in Chapter 5. I abandoned the term lower bound.

@@

It is true that Quincunx requires the random input variables to be independent and identically distributed. That's why I applied a blackbox fuzzing instead of a coverage-guided fuzzing. As long as each time we get a random input from the whole input space (Populations) that is independent of the previous input, the input variables should satisfy the i.i.d. assumption. For AES-128 encryption, each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values follows the i.i.d. assumption.

The situation is a little different for a machine learning library. In the dissertation, we evaluated Quincunx on a deep learning model. Each time, we randomly select an item from a dataset (Samples). If the dataset is biased, then we can not get correct results. The good news is that the most well-known data in machine learning is i.i.d. i.i.d. is the foundation of supervised machine learning algorithms. In my dissertation, we used MINIST, a well-known handwriting dataset. We believe the dataset is i.i.d.

@@

Dr. Larus helped me fix many grammar issues. I have revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.

>>>>

I have a few choices to address the limitation. First, I can use static methods (verification or static program analysis). Although I am interested in static analysis, I am not a big fan of current static analysis tools, especially for side-channel research. There are many papers on static side-channel analysis. Nearly all of these tools are used to prove the absence of side-channel leakages. However, most of them have high false-positive rates.

On the other hand, there are many success stories with dynamic tools (e.g., SAGE, AFL, Valgrind) in recent years. In particular, fuzzing is becoming a hot trend these years, especially after DARPA CGC in 2016. The fuzzing method is suitable for a task such as side-channel detection. If a program executes two different code paths or accesses two different variables with two different input values, the program is vulnerable to side-channel attacks. When we report the leakages sites to developers, we can tell them the two inputs. Developers can quickly reproduce the leakage sites with the inputs.  Interestingly, there are a few (not many) related papers. That's why I used fuzzing at the beginning of the project.

@@

It is possible to extend the quantification part to include other side-channel signals (e.g., Sound, CPU usages, EM signals). The key is to model the noises properly. In my dissertation, we assume that an attacker can have a noise-free observation. While a noise-free observation is possible for some address-based side-channel attacks, the assumption is too ideal for many other side-channel attacks. The good news is that there are some mature methods in information theory to model noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a computable method to estimate the information that can be reliably transferred over a channel between secret data and attackers' observations. From a research project aspect, I hope to have a stronger motivation before starting the project. 
\item \textbf{A bits vs. Q bits. Lower bounds?
       Improve the presentation
       Make the comparison more meaningful
       Etc.}

@@

c. I agree with Dr. Liu's comments that the quantification metrics in Chapter 4 and Chapter 5 are different. The reason that I compare them together in Table 5.3 is that they have the same dimensional unit (bit) under the dimensional analysis. I have removed the comparison from the evaluation section in the current version.

@@

a. I revised the description in Chapter 5. I avoided the use of ``term lower bound''.

@@

It is true that Quincunx requires the input variables to be independent and identically distributed. That's why I applied a blackbox fuzzing instead of a coverage-guided fuzzing. As long as each time we get a random input from the whole input space (Populations) that is independent of the previous input, the input variables should satisfy the i.i.d. assumption. For AES-128 encryption, each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values follows the i.i.d. assumption.

The situation is a little different for a machine learning library. In my dissertation, we also evaluated Quincunx on a deep learning model. Each time, we randomly select an item from a dataset (Samples). If the dataset is biased, then we can not get correct results. The good news is that the most well-known data in machine learning is i.i.d. i.i.d. is the foundation of supervised machine learning algorithms. In my dissertation, we used MINIST, a well-known handwriting dataset. We believe the dataset is i.i.d..

@@

Dr. Larus helped me fix many grammar issues. I also revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.
